Market Simulator

### 2020-08-05 analysis/05_market_simulator.Rmd
Commented out Sidebar. Change page layout from Pages to Rows. Added tabset placeholders

Persona Inputs {.sidebar}
=================================================

## Persona Inputs

```{r sidebar inputs, echo=FALSE}

# selectInput("model_choice", 
#             label = "Select Model:",
#             choices = c("public_political_social_charity_demo"))

selectInput("charity_importance", 
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("trust_in_charity", 
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("donation_frequency", 
         label = "Donation Frequency:",
         choices = c('Once a week', 
                     'Once a Month',
                     'Once every three months',
                     'Once every six months', 
                     'Once a year', 
                     'Once every few years',
                     'Never'))

selectInput("donation_amount", 
         label = "Donation Amount:",
         choices = c("$1-$49", 
                     '$50-$99', 
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("volunteer_12", 
         label = "Volunteered in last 12 Months:",
         choices = c("Yes", "No"))

selectInput("volunteer_frequency", 
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months', 
                     'Once every six months', 
                     'Once a year', 
                     'Once every few years',
                     'Never'))

selectInput("personal_activism", 
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved', 
                     'Moderately involved', 
                     'Slightly involved',
                     'Never involved'))

selectInput("family_activism", 
         label = "Family Activism:",
         choices = c('Extremely involved', 
                     'Very involved', 
                     'Moderately involved', 
                     'Slightly involved',
                     'Never involved'))

selectInput("religious_member", 
         label = "Church Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("sport_member", 
         label = "Sport or Recreational Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("art_member", 
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("labor_member", 
         label = "Labor Union Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("political_member", 
         label = "Political Party Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("environmental_member", 
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("professional_member", 
         label = "Professional Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("humanitarian_member", 
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("consumer_member", 
         label = "Consumer Org. Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("religious_member", 
         label = "Church Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("other_member", 
         label = "Other Org. Membership:",
         choices = c('Active Member', 
                     'Inactive Member', 
                     "Don't belong"))

selectInput("national_news", 
         label = "Follow national news:",
         choices = c('Multiple times a day', 
                     'Every day', 
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("international_news", 
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("news_medium", 
         label = "Medium to follow news:",
         choices = c('TV', 
                     'Print', 
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"))

selectInput("international_news", 
         label = "Follow international news:",
         choices = c('Multiple times a day', 
                     'Every day', 
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("follow_gov", 
         label = "Follow government & public affairs:",
         choices = c('Most of the time', 
                     'Some of the time', 
                     "Only now and then",
                     "Hardly at all"))

selectInput("travel_developing", 
         label = "Travel to developing country:",
         choices = c('Yes', 'No'))

selectInput("polical_pref", 
         label = "Polical views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("institution_trust", 
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("others_charitable", 
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("worship_attendance", 
         label = "Worship service attendance:",
         choices = c('Multiple times a week', 
                     'Once a week', 
                     "Once a month",
                     "Once a year",
                     "Never"))

selectInput("religion_importance", 
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

selectInput("religion", 
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other'))

selectInput("gender", 
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other"))

selectInput("marital_status", 
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"))

selectInput("education", 
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))

selectInput("income", 
         label = "Income:",
         choices = c('Less than $10,000', 
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("race", 
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other'), 
         multiple = TRUE)

selectInput("education", 
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))

selectInput("age", 
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

Market Share Per Persona
==================================================

### Market Share Per Persona

@@

Persona 1 
====================================================

Market Share and Expected Utility
--------------------------------------------------

@@

Organization Market Share
-------------------------------------
### Amnesty International Market Share

@@

@@

@@

@@

@@

Bottom of page buffer
-----------------------------------------------

@@

Persona 2
===============================================

Market Share
--------------------------------------------------
```{r plot persona 2}
renderPlotly({
  choice = df()

@@

Persona 3
===============================================

Market Share 
------------------------------------------------
```{r plot persona 3}
renderPlotly({
  choice = df()

@@

<!-- Expected Donors {.tabset .tabset-fade} -->
<!-- ------------------------------------- -->
<!-- ### Amnesty International Expected Donors -->

<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
<!--   gauge(ai_rate,  -->
<!--         min = 0,  -->
<!--         max = 100, -->
<!--         gaugeSectors(colors = "#FFC30B"), -->
<!--         symbol = "%") -->
<!-- }) -->
<!-- ``` -->

>>>>

<!-- Persona Inputs {.sidebar} -->
<!-- ================================================= -->

<!-- ## Persona Inputs -->

<!-- ```{r sidebar inputs, echo=FALSE} -->

<!-- # selectInput("model_choice",  -->
<!-- #             label = "Select Model:", -->
<!-- #             choices = c("public_political_social_charity_demo")) -->

<!-- selectInput("charity_importance",  -->
<!--           label = "Charity Importance:", -->
<!--           choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("trust_in_charity",  -->
<!--             label = "Charity Trust:", -->
<!--             choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("donation_frequency",  -->
<!--          label = "Donation Frequency:", -->
<!--          choices = c('Once a week',  -->
<!--                      'Once a Month', -->
<!--                      'Once every three months', -->
<!--                      'Once every six months',  -->
<!--                      'Once a year',  -->
<!--                      'Once every few years', -->
<!--                      'Never')) -->

<!-- selectInput("donation_amount",  -->
<!--          label = "Donation Amount:", -->
<!--          choices = c("$1-$49",  -->
<!--                      '$50-$99',  -->
<!--                      '$100-$499', -->
<!--                      '$500-$999', -->
<!--                      '$1,000-$4,999', -->
<!--                      '$5,000-$9,999', -->
<!--                      '$10,000+')) -->

<!-- selectInput("volunteer_12",  -->
<!--          label = "Volunteered in last 12 Months:", -->
<!--          choices = c("Yes", "No")) -->

<!-- selectInput("volunteer_frequency",  -->
<!--          label = "Volunteer Frequency:", -->
<!--          choices = c('Once a week', -->
<!--                      'Once a Month', -->
<!--                      'Once every three months',  -->
<!--                      'Once every six months',  -->
<!--                      'Once a year',  -->
<!--                      'Once every few years', -->
<!--                      'Never')) -->

<!-- selectInput("personal_activism",  -->
<!--          label = "Personal Activism:", -->
<!--          choices = c('Extremely involved', -->
<!--                      'Very involved',  -->
<!--                      'Moderately involved',  -->
<!--                      'Slightly involved', -->
<!--                      'Never involved')) -->

<!-- selectInput("family_activism",  -->
<!--          label = "Family Activism:", -->
<!--          choices = c('Extremely involved',  -->
<!--                      'Very involved',  -->
<!--                      'Moderately involved',  -->
<!--                      'Slightly involved', -->
<!--                      'Never involved')) -->

<!-- selectInput("religious_member",  -->
<!--          label = "Church Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("sport_member",  -->
<!--          label = "Sport or Recreational Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("art_member",  -->
<!--          label = "Art, Music, or Educational Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("labor_member",  -->
<!--          label = "Labor Union Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("political_member",  -->
<!--          label = "Political Party Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("environmental_member",  -->
<!--          label = "Enviornmental Org. Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("professional_member",  -->
<!--          label = "Professional Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("humanitarian_member",  -->
<!--          label = "Humanitarian Org. Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("consumer_member",  -->
<!--          label = "Consumer Org. Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("religious_member",  -->
<!--          label = "Church Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("other_member",  -->
<!--          label = "Other Org. Membership:", -->
<!--          choices = c('Active Member',  -->
<!--                      'Inactive Member',  -->
<!--                      "Don't belong")) -->

<!-- selectInput("national_news",  -->
<!--          label = "Follow national news:", -->
<!--          choices = c('Multiple times a day',  -->
<!--                      'Every day',  -->
<!--                      "Once a week", -->
<!--                      "Hardly ever", -->
<!--                      "Never")) -->

<!-- selectInput("international_news",  -->
<!--          label = "Follow international news:", -->
<!--          choices = c('Always', -->
<!--                      "Sometimes", -->
<!--                      "Never")) -->

<!-- selectInput("news_medium",  -->
<!--          label = "Medium to follow news:", -->
<!--          choices = c('TV',  -->
<!--                      'Print',  -->
<!--                      "Online", -->
<!--                      "Social Media", -->
<!--                      "Radio", -->
<!--                      "Email newsletters", -->
<!--                      "News app")) -->

<!-- selectInput("international_news",  -->
<!--          label = "Follow international news:", -->
<!--          choices = c('Multiple times a day',  -->
<!--                      'Every day',  -->
<!--                      "Once a week", -->
<!--                      "Hardly ever", -->
<!--                      "Never")) -->

<!-- selectInput("follow_gov",  -->
<!--          label = "Follow government & public affairs:", -->
<!--          choices = c('Most of the time',  -->
<!--                      'Some of the time',  -->
<!--                      "Only now and then", -->
<!--                      "Hardly at all")) -->

<!-- selectInput("travel_developing",  -->
<!--          label = "Travel to developing country:", -->
<!--          choices = c('Yes', 'No')) -->

<!-- selectInput("polical_pref",  -->
<!--          label = "Polical views from liberal to conservative:", -->
<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("institution_trust",  -->
<!--          label = "Political institution trust from none to complete:", -->
<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("others_charitable",  -->
<!--          label = "People should be more charitable:", -->
<!--          choices = c("0", '1', '2', '3','4','5','6','7')) -->

<!-- selectInput("worship_attendance",  -->
<!--          label = "Worship service attendance:", -->
<!--          choices = c('Multiple times a week',  -->
<!--                      'Once a week',  -->
<!--                      "Once a month", -->
<!--                      "Once a year", -->
<!--                      "Never")) -->

<!-- selectInput("religion_importance",  -->
<!--          label = "Importance of religion:", -->
<!--          choices = c('Extremely important', -->
<!--                      'Very important', -->
<!--                      'Moderately important', -->
<!--                      'Slightly important', -->
<!--                      'Not at all important')) -->

<!-- selectInput("religion",  -->
<!--          label = "Religion:", -->
<!--          choices = c('Catholic', -->
<!--                      'Protestant', -->
<!--                      'Christian Orthodox', -->
<!--                      'Jewish', -->
<!--                      'Muslim', -->
<!--                      'Sikh', -->
<!--                      'Hindu', -->
<!--                      'Buddhist', -->
<!--                      'Atheist', -->
<!--                      'Other')) -->

<!-- selectInput("gender",  -->
<!--          label = "Gender:", -->
<!--          choices = c("Male", -->
<!--                      "Female", -->
<!--                      "Transgender", -->
<!--                      "Prefer not to say", -->
<!--                      "Other")) -->

<!-- selectInput("marital_status",  -->
<!--          label = "Marital Status:", -->
<!--          choices = c("Married", -->
<!--                      "Widowed", -->
<!--                      "Divorced", -->
<!--                      "Separated", -->
<!--                      "Never married")) -->

<!-- selectInput("education",  -->
<!--          label = "Education:", -->
<!--          choices = c("Less than high school", -->
<!--                      "High school", -->
<!--                      "Some college", -->
<!--                      "2 year degree", -->
<!--                      "4 year degree", -->
<!--                      "Graduate degree", -->
<!--                      "Doctorate")) -->

<!-- selectInput("income",  -->
<!--          label = "Income:", -->
<!--          choices = c('Less than $10,000',  -->
<!--                      '$10,000 to $19,999', -->
<!--                      '$20,000 to $29,999', -->
<!--                      '$30,000 to $39,999', -->
<!--                      '$40,000 to $49,999', -->
<!--                      '$50,000 to $59,999', -->
<!--                      '$60,000 to $69,999', -->
<!--                      '$70,000 to $79,999', -->
<!--                      '$80,000 to $89,999', -->
<!--                      '$90,000 to $99,999', -->
<!--                      '$100,000 to $149,999', -->
<!--                      '$150,000 to $199,999', -->
<!--                      '$200,000 to $299,999', -->
<!--                      '$300,000 or more')) -->

<!-- selectInput("race",  -->
<!--          label = "Race(s):", -->
<!--          choices = c('White', -->
<!--                      'Black or African American', -->
<!--                      'American Indian or Alaska Native', -->
<!--                      'Asian', -->
<!--                      'Native Hawaiian or Pacific Islander', -->
<!--                      'Other'),  -->
<!--          multiple = TRUE) -->

<!-- selectInput("education",  -->
<!--          label = "Education:", -->
<!--          choices = c("Less than high school", -->
<!--                      "High school", -->
<!--                      "Some college", -->
<!--                      "2 year degree", -->
<!--                      "4 year degree", -->
<!--                      "Graduate degree", -->
<!--                      "Doctorate")) -->

<!-- selectInput("age",  -->
<!--          label = "Age:", -->
<!--          choices = c('Under 18', -->
<!--                      '18 - 24', -->
<!--                      '25 - 34', -->
<!--                      '35 - 44', -->
<!--                      '45 - 54', -->
<!--                      '55 - 64', -->
<!--                      '65 - 74', -->
<!--                      '75 - 84', -->
<!--                      '85 or older')) -->

<!-- ``` -->

@@

Market Share Per Persona 
--------------------------------------

@@

Persona 1 (change this to Org 1) {.tabset .tabset-fade}
--------------------------------------------------

### Market Share Chart Persona 1
<!-- Might get rid of this graph -->

@@

### Amnesty International Market Share

@@

Organizations {.tabset .tabset-fade}
-------------------------------------
### Amnesty International

@@

```{r echo=FALSE}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})
```

### Greenpeace

@@

### Oxfam

@@

### Red Cross

@@

@@

Persona 2 {.tabset .tabset-fade}
--------------------------------------------------

### Market Share Persona 2

```{r plot persona 2}
renderPlotly({
  choice = df()

@@

Persona 3 {.tabset .tabset-fade}
--------------------------------------------------

### Market Share Persona 3
```{r plot persona 3}
renderPlotly({
  choice = df()

@@

Expected Donors {.tabset .tabset-fade}
-------------------------------------
### Amnesty International Expected Donors

```{r echo=FALSE}
renderGauge({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})
```
